VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-24 snapshot_system/paper_abs.tex
revised

\begin{abstract}
Data deduplication has been widely used for cloud data backup
because of excessive redundant content blocks. Common techniques use dirty bits to detect
the version  change and  perform global fingerprint comparison to remove duplicates
across virtual machines. However, letting a duplicate data block be shared
by many virtual machines creates data dependence and is less fault-resilient. 
%This paper studies the impact of deduplication on 
%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
%and fault isolation 
This paper proposes a VM-centric backup service on a converged  storage cluster architecture
and  strikes a balance for better fault isolation with competitive  deduplication efficiency.
It localizes deduplication as much as possible within each 
virtual machine, guided by similarity
search and associates  underlying file blocks with one VM for most cases.
It restricts global deduplication to popular chunks with extra replication support.
This VM-centric scheme also has  an advantage of   using less  computing resources for fingerprint comparison and simplifies snapshot deletion, suitable for a collocated backup service 
on a non-dedicated cluster architecture.
This  paper  describes an evaluation of this scheme to assess  its deduplication 
efficiency and fault resilience.

>>>>

\begin{abstract}
Data deduplication has been widely used for cloud data backup
because of excessive redundant content blocks. Common techniques 
%use dirty bits to detect
%the version  change and  
perform fingerprint comparison to remove duplicates
across virtual machines. However, letting a duplicate data block be shared
by many virtual machines creates data dependence and is less fault-resilient. 
%This paper studies the impact of deduplication on 
%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
%and fault isolation 
This paper proposes a VM-centric backup service on a converged  storage cluster architecture
and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
It localizes deduplication as much as possible within each 
virtual machine, guided by similarity
search, and it restricts global deduplication under popular chunks with extra replication support.
It associates  underlying file blocks with one VM for most cases
and proposes an approximate method for fast and simplified snapshot deletion.
This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for a collocated 
backup service on a non-dedicated cluster architecture.
This  paper  describes an evaluation of this scheme to assess  its deduplication 
efficiency and fault resilience.

### 2014-01-24 snapshot_system/paper_analysis.tex
revised

We analyze the impact of replication degree for PDS and non-PDS data items.
The parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
The replication degree of the backup storage 
is $r$ for regular file system blocks and $r=3$ is a typical setting in distributed
file systems~\cite{googlefs03,hdfs10}.
Since $\sigma$ is small (e.g.  2\% in our experiments),  
the impact of replication on storage increase is very small even 
when choosing  $r_c/r$ ratio as 2 or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the VC and VO approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
%We use an FSB rather than a deduplication
%data chunk as our unit of failure because the DFS keeps
%file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probability of losing a snapshot FSB of a VM by
estimating the number of file system blocks per VM in each approach.
%As illustrated in Figure~\ref{fig:share},
%we build a bipartite graph representing the association from unique file system blocks
%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
%if this block is used by the VM.

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in the VC
and VO approaches. We use an FSB rather than data chunk as our unit of failure
because the DFS keeps file system blocks as its base unit of storage, and in
the case of 64MB FSBs and 4KB chunks, there are 16K chunks per block. In VC
we assign extra replication to the PDS blocks, while in VO the replication
degree is fixed.

We could consider a third approach (call it VO+), adopting the VO approach, and
then relying on filesystem features to provide extra replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The problem with this VO+ approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system. Because the popular blocks
are dispersed, there are very few popular FSBs. The end result is that we
either have to add extra replication on unpopular chunks to ensure the popular
chunks have sufficient replication, or we have to accept a reduced replication
factor on popular chunks. This explains why we must separate the PDS and
non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
can be stored on the same DFS).

For VC, each VM has an average number $N_1$ of non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. 
%Let $s$ be the average number of chunks per file system block, 
%$V$ be the average number of VMs hosted on each machine. 
Then, 
\[
V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V pN_2 s  \approx c_u \sigma V_c.
\]

>>>>

We analyze the impact of the above VM centric design on fault isolation and compare it
with a VM oblivious design.
Let $r$ be the replication degree of standard file blocks in the underlying backup storage. 
$r=3$ is a typical setting in distributed file systems~\cite{googlefs03,hdfs10}.
Let $r_c$ be the replication degree of file blocks for PDS. 
Additional parameters used in our analysis below are defined in Table~\ref{tab:symbol}. 
%The replication degree of the backup storage 
%is $r$ for regular file system blocks and 
%Since $\sigma$ is small (e.g.  2\% in our experiments),  
%the impact of replication on storage increase is very small even 
%when choosing  $r_c/r$ ratio as 2 or 3.

@@

Now we  assess  the impact of losing $d$ machines 
to the VM centric and oblivious approaches.  
A large $r_c/r$ ratio can have a positive impact on full availability of VM snapshot blocks.
%We use an FSB rather than a deduplication
%data chunk as our unit of failure because the DFS keeps
%file system blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we estimate
the number of file system blocks per VM and the probability of losing a snapshot file system 
block of a VM in each approach as follows.
%As illustrated in Figure~\ref{fig:share},
%we build a bipartite graph representing the association from unique file system blocks
%to their corresponding VMs in each approach. An association edge is  drawn  from an FSB to a VM 
%if this block is used by the VM.

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in two 
approaches. We use a file system block rather than data chunk as our unit of failure
because the underlying file system keeps file system blocks as its base unit of storage, and in
the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
we assign extra replication to the PDS blocks, while for VM oblivious, the replication
degree is fixed.

\comments{
%Moved up in the strategy subsection
We could consider a third approach (call it VO+), adopting the VO approach, and
then relying on filesystem features to provide extra replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The problem with this VO+ approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system. Because the popular blocks
are dispersed, there are very few popular FSBs. The end result is that we
either have to add extra replication on unpopular chunks to ensure the popular
chunks have sufficient replication, or we have to accept a reduced replication
factor on popular chunks. This explains why we must separate the PDS and
non-PDS data in our system to achieve the desired $r_c/r$ ratio (though both
can be stored on the same DFS).
}
For VC, each VM has an average number $N_1$ of non-PDS FSBs
and  has  an average of  $N_2$ PDS FSBs. 
Each non-PDS FSB is associated with one VM
 and  we denote that PDS FSBs are
shared by an average of $V_c$ VMs. 
%Let $s$ be the average number of chunks per file system block, 
%$V$ be the average number of VMs hosted on each machine. 
Then, 
\[
V pN_1 s  \approx c-E_c(c-c_u) - c_u\sigma\; \mbox{ and } \; 
V pN_2 s  \approx c_u \sigma V_c.
\]

### 2014-01-24 snapshot_system/paper_background.tex
revised

Figure~\ref{fig:collocated} illustrates a converged cloud architecture where
each commodity server hosts a number of virtual machines and storage of these servers
is clustered using a distributed file system (DFS)~\cite{googlefs03,hdfs10}.
Each physical machine 
each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
This architecture does not use a seperate  backup facility for a lower cost and 
reduces the network bandwidth consumption in transferring the raw data for backup. 
A backup sevice runs on these commodity servers and stores deduplicated data  in  the storage in this cluster or in
a seperate storage cluster.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/colocated-arch}
    \caption{Collocated VM Backup System.}
    \label{fig:collocated}
\end{figure}

Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  It is expensive to compare a large number of chunk fingerprints
and several techniques have been proposed to speedup. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  
%An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{wei2013}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in a cloud  cluster environment considered in this paper.
Our consideration is discussed below.
%VM dependence minimization during deduplication and file system block management.
\begin{itemize}
\item {\em Deduplication localization.}
Because a data chunk is compared with fingerprints collected from all VMs during
the deduplication process, only one copy of duplicates is stored in the storage,
this artificially creates data dependencies among different VM users. 
Content sharing via deduplication affects fault isolation since machine failures happen periodically 
in a large-scale cloud and
loss of a small number of shared data chunks can 
cause the unavailability of snapshots for a large number of virtual machines.
Localizing the impact of deduplication can increase fault isolation and resilience.
Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
discouraged. 
Another disadvantage of sharing is that it complicates snapshot deletion, 
which  occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for deletion, but still carries a significant cost
to count if a data chunk is still shared by other snapshots. 
Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
\item{\em  Management of file system blocks.}
The file system block (FSB) size in a distributed file system such as  Hadoop and GFS is uniform and large (e.g.  64MB),
while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
Packaging data chunks to an FSB can create more data dependencies among VMs
since a file system block can be shared by even more VMs.
Thus we need to consider a minimum association of FSBs to VMs in the packaging process.

\item {\em Low resource usage in a nondedicated cloud cluster.}
Since the cluster we consider is shared by many cloud services,
low resource usage of deduplication is desired so that
there is  a minimal impact to the other existing cloud services.
The key resource for global comparison  is memory for storing the fingerprints. 
We will consider the approximation techniques with reduced memory consumption. 
\end{itemize}

We call the traditional deduplication approach as   VM-oblivious (VO)
because they compare fingerprints of snapshots without consideration of VMs.
With the above  considerations in mind, we study a 
VM-centric approach (called VC)
for a collocated backup service with resource usage friendly
to the existing applications.

>>>>

Figure~\ref{fig:collocated} illustrates a converged cloud architecture where
each commodity server hosts a number of virtual machines and storage of these servers
is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
Each physical machine 
each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
%This architecture does not use a seperate  backup facility for a lower cost and 
%reduces the network bandwidth consumption in transferring the raw data for backup. 
A backup sevice may collocate with other cloud services on these commodity servers and 
stores deduplicated data  in  the storage in this cluster or in
a seperate storage cluster.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/colocated-arch}
    \caption{VM snapshot backup running on a converged cloud cluster.}
    \label{fig:collocated}
\end{figure}

File backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  It is expensive to compare a large number of chunk fingerprints
and several techniques have been proposed to speedup. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks  which may be
accessed.  
%An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,Srinivasan2012}
and a parallel batch solution for cluster-based deduplication is 
studied in ~\cite{wei2013}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in a cloud  cluster environment considered in this paper.
Our consideration is discussed below.
%VM dependence minimization during deduplication and file system block management.
\begin{itemize}
\item {\em Deduplication localization.}
Because a data chunk is compared with fingerprints collected from all VMs during
the deduplication process, only one copy of duplicates is stored in the storage,
this artificially creates data dependencies among different VM users. 
Content sharing via deduplication affects fault isolation since machine failures happen periodically 
in a large-scale cloud and
loss of a small number of shared data chunks can 
cause the unavailability of snapshots for a large number of virtual machines.
Localizing the impact of deduplication can increase fault isolation and resilience.
Thus from the fault tolerance point of view,  duplicate sharing among multiple VMs is 
discouraged. 
Another disadvantage of sharing is that it complicates snapshot deletion, 
which  occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for deletion, but still carries a significant cost
to count if a data chunk is still shared by other snapshots. 
Localizing deduplication can  minimize data sharing and simplify deletion while sacrificing 
deduplication efficiency, and  can facilitate parallel execution of snapshot operations.
\item{\em  Management of file system blocks.}
The file system block (FSB) size in a distributed file system such as  Hadoop and Google file system
 is uniform and large (e.g.  64MB),
while the data chunk in a typical deduplication system is of a non-uniform size with 4KB or 8KB on average.
Packaging data chunks to an FSB can create more data dependencies among VMs
since a file system block can be shared by even more VMs.
Thus we need to consider a minimum association of FSBs to VMs in the packaging process.

\item {\em Low resource usage in a nondedicated cloud cluster.}
When a backup service collocates with other cloud services as illustrated in Figure~\ref{fig:collocated},
low resource usage of deduplication is desired so that
there is  a minimal impact to the other existing cloud services.
The key resource for global comparison  is memory for storing the fingerprints.
During snapshot deltion, reference counting for all unique blocks used in all VMs requires a significant resource usage
too.  Thus we seek for the low-profile techniques with approximation and low resource consumption. 
\end{itemize}

We call the traditional deduplication approach as   VM-oblivious (VO)
because they compare fingerprints of snapshots without consideration of VMs.
With the above  considerations in mind, we study a 
VM-centric approach (called VC)
for a collocated backup service with resource usage friendly
to the existing applications in a converged clustr architecture.

### 2014-01-24 snapshot_system/paper_conc.tex
add paper files
revised

\section{Conclusion}
\label{sect:conclusion}
In this paper we propose a collocated backup service built on
the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The key contribution is a VM-centric deduplication scheme to 
maximize fault isolation with only a slight tradeoff in deduplication efficiency.
Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
while global deduplication with a small common data set eliminates popular duplicates.
VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
The design places a special consideration for low-resource usages as a collocated cloud service.
Evaluation using  VM backup data shows that VC strikes a tradeoff and 
can accomplish 96.33\% or 96.9\% of what complete global
deduplication can do.  The availability of snapshots increases substantially with 
a small replication overhead for popular inter-VM chunks.

>>>>

\section{Conclusion}
\label{sect:conclusion}
%In this paper we propose a collocated backup service built on
%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency using
a small amount of system resource.
Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
can accomplish 96.33\% or 96.9\% of what complete global
deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
low-resource usage.  The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block.
%Currently we are studying how the

%Similarity guided local search reduces cross-VM data dependency and exposes more parallelism  
%while global deduplication with a small common data set eliminates popular duplicates.
%VM-specific file block packing also enhances fault tolerance by reducing data dependencies.
%The design places a special consideration for low-resource usages as a collocated cloud service
%and

### 2014-01-24 snapshot_system/paper_dedup.tex
revised

\subsection{Key VC  Strategies}
\label{sect:vc-strategies}
%\begin{itemize}
%\item 
\textbf{VM-specific local duplicate search within similar segments.}
We start with the changed block tracking approach in a coarse grain segment level.
In our implementation with Xen on an Alibaba platform, the segment size is 2MB
and the device driver is extended to support tracking changed segments using a dirty bitmap. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement such changed block tracking feature.

@@

>>>>

\subsection{VM centric  strategies}
\label{sect:vc-strategies}
%\begin{itemize}
%\item 
\textbf{VM-specific local duplicate search within similar segments.}
We start with the changed block tracking approach in a coarse grain segment level.
In our implementation with Xen on an Alibaba platform, the segment size is 2MB
and the device driver is extended to support tracking changed segments using a dirty bitmap. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement such changed block tracking feature.

@@

It should not be noted that one could consider 
to rely on filesystem features to provide more replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The main problem with this  approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system.  We would
have to add extra replication to each file block as long as it contains a popular chunk.

%factor on popular chunks. This explains why we must separate the PDS and
%non-PDS data in our system to acheive the desired $r_c/r$ ratio (though both
%can be stored on the same DFS).

### 2014-01-24 snapshot_system/paper_del.tex
revised

In a busy VM cluster, snapshot deletions can occur frequently.
Deduplication complicates the deletion process because space saving relies on the sharing of data
and it requires the global references to deleted chunks to be identified before they can be safely removed.
%The complexity of our distributed environment obviates reference counting as an option,
%and While we can use the mark-and-sweep, 
%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.

We seek a fast solution with low resource usage to delete snapshots and
our VM-centric design simplifies the deletion process. 
Since PDS is small and separated, we can focus on  unreferenced non-PDS chunks within each VM. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
Another resource-saving strategy we propose is
an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.
The algorithm contains three aspects.

\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to  estimation of VM image size,
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during the periodic leakage repair stage described below.

>>>>

Snapshot deletions can occur frequently since old snapshots become less useful.
General deduplication complicates the deletion process because sharing of duplicates
requires a global refence counting to identify if  a chunk can be  safely removed without any reference.
%The complexity of our distributed environment obviates reference counting as an option,
%and While we can use the mark-and-sweep, 
%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
Since our VM-centric design restricts sharing of data chunks only to a small dataset,
we can greatly simplify the deletion process by 
focusing on  unreferenced non-PDS chunks within each VM. 
This process can be conducted by independent among VMs, and thus results in  a simpler flow control and 
lower resource usage. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.

We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.
The algorithm contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to  estimation of VM image size,
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during the periodic leakage repair stage described below.

### 2014-01-24 snapshot_system/paper_intro.tex
revised

One of popular architectures for building cloud services
is a converged architecture that leverages commodity servers with software clustered storage and network, without 
requiring network storage (e.g. SAN or NAS)~\cite{NutanixPaper}. 
Leading cloud platform companies such as Google, Amazon, Alibaba,
Microsoft Azure  have built a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
Frequent  snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

@@

A common technique for VM snapshot deduplication is    version-based detection that identifies file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Another popular technique is to conduct global fingerprint  comparison to identify duplicates that exist
among all files~\cite{Guo2011,Dong2011,extreme_binning09}.
Because of highly repetitive content in snapshot backup,
most data chunks are shared by many virtual machines.  Failure of a few shared data chunks can have a 
broad effect and many snapshots of virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.

The key contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
virtual machines, and   propose a VM-centric approach that localizes deduplication as much as possible 
and restrict global deduplication only to a limited set of most popular blocks.
Local deduplication also uses similarity-guided elimination to improve the deduplication coverage.
Since the file system block size is normally bigger than the average data chunk size used for deduplication,
we also package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
Because data sharing is restricted, 
this VM-centric approach can also simplify the snapshot deletion process and reduce the overall resource usage, which
is suitable when the backup service with deduplication is collocated with other services running on a shared compute and storage
cluster.
We have evaluated this VM-centric approach using  a prototype system that runs a cluster of Linux machines with Xen and 
a standard distributed file system for the backup storage. 
%This approach localizes duplicate detection within each VM  
%By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
%this scheme can afford to allocate extra replicas of these shared chunks for better
%fault resilience while sustaining competitive deduplication efficiency.

>>>>

One of emerging architectures for building cloud services
is a converged architecture that leverages commodity servers with software clustered storage, without 
requiring network storage (e.g. ~\cite{NutanixPaper}). 
Leading cloud platform companies such as Google, Amazon, Alibaba,
Microsoft Azure  have built a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers.
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines 
%as  instances of a guest operating system 
and their  virtual disks are represented as virtual disk image files in the host operating system.
Frequent  snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

@@

While version-based detection  has been used to  identify file  blocks that have not 
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011},
a popular technique for deduplicatioon is to 
conduct fingerprint  comparison and identify duplicates that exist
among all files~\cite{Guo2011,Dong2011,extreme_binning09}. 
Because of highly repetitive content in snapshots from different VMs,
many data chunks are shared by virtual machines.  
Failure of a few shared data chunks can have a 
broad effect and snapshots of these virtual machines could be affected.
The previous work in deduplication focuses on the efficiency and approximation of
fingerprint comparison, and has not addressed fault tolerance issues  together with deduplication.
Thus we seek a method that strikes a balance between fault isolation and deduplication efficiency.

The main contribution of this work is to evaluate the fault tolerance  impact of popular data blocks shared by many
virtual machines, and   propose a VM-centric approach that localizes deduplication as much as possible 
and restricts global deduplication only to a limited set of most popular blocks.
Local deduplication also uses similarity-guided elimination to improve the deduplication coverage.
Since the file system block size is normally bigger than the average data chunk size used for deduplication,
we package data chunks from the same VM into a file system block as much as possible to improve fault isolation.
Because data sharing is restricted, 
this VM-centric approach reduces the overall resource usage significantly during backup and
simplifies the snapshot deletion process. This low-resource design
is suitable when the backup service with deduplication is collocated with other services running on a shared compute and storage
cluster.  We have evaluated this VM-centric approach using  a prototype system.
% that runs a cluster of Linux machines with Xen and a standard distributed file system for the backup storage. 
%This approach localizes duplicate detection within each VM  
%By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
%this scheme can afford to allocate extra replicas of these shared chunks for better
%fault resilience while sustaining competitive deduplication efficiency.
